\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and the Sliding Window Filter

### 2015-03-02 Report/project_report.tex
Updated kitti result

\author{Lee Clement$^{1}$ and Valentin Peretroukhin$^{1}$% <-this % stops a space
%\thanks{*This work was not supported by any organization}% <-this % stops a space
\thanks{$^{1}$Institute for Aerospace Studies,
        University of Toronto, Toronto, ON, Canada
        {\tt \{lee.clement, valentin.peretroukhin\} @robotics.utias.utoronto.ca}
        }%
}

>>>>

\author{Lee Clement, Valentin Peretroukhin, Jacob Lambert, and Jonathan Kelly% <-this % stops a space
%\thanks{*This work was not supported by any organization}% <-this % stops a space
\thanks{All authors are at the Institute for Aerospace Studies,
        University of Toronto, Canada
        {\tt \{lee.clement, v.peretroukhin, jacob.lambert\}@mail.utoronto.ca, jkelly@utias.utoronto.ca}
        }%
}
